SecureIt\\ Wireless networks project\\ 2012/2013

### 2012-12-26 relazioni/wireless/paper.tex
Fixati una serie di bug di chiusura e apertura applicazione, integrata relazione wireless con nuove screenshot

\title{SecureIt: home security has never been so easy\\
Anno Accademico 2011/2012}

\author{
\IEEEauthorblockN{Luca Bonato, Marco Ziccardi}
\IEEEauthorblockA{Corso di studi in Informatica\\
Facoltà di Scienze MM.FF.NN.\\
Università degli Studi di Padova\\
Email: \{lohathe,marco.ziccard\}@gmail.com}
}

@@

@@

\subsection{Delegated authorization}
In the authentication phase a \texttt{delegated\allowbreak\_access\allowbreak\_token} is retrieved in order to not use the same token for both direct and delegated authentication. However such a token should not be shared with other devices and in order to do so a little protocol has been developed.\\
The presented protocol is slightly inspired by Kerberos (\texttt{[1]}) and is based on three messages:\\
\begin{itemize}
	\item \texttt{HelloMessage}: sent from the requesting phone, simply contains a timestamp and the phone's identifier
	\item \texttt{KeyRequest}: sent from a delegated phone to the requesting one, contains latitude, longitude and a timestamp
	\item \texttt{KeyResponse}: sent from the requesting phone, contains an \texttt{authorization\_key} based on \texttt{delegated\_access\_token}, latitude, longitude and received timestamp
\end{itemize}

@@

\texttt{authorization\_key} is computed via \texttt{AES} password encryption, using as password the value \texttt{delegated\_access\_token} and encrypting the \texttt{JSON} string:
\begin{lstlisting}[language=Java, caption=JSON encrypted with AES]
{"lat": "latitude",
 "long": "longitude",
 "timestamp": "timestamp"}
\end{lstlisting}

@@

\begin{lstlisting}[language=Java, caption=AES password encryption]
SecretKeySpec key = new SecretKeySpec(password.getBytes(), "AES");
AlgorithmParameterSpec paramSpec = new IvParameterSpec(password.substring(0, 16).getBytes());
Cipher cipher;
cipher = Cipher.getInstance("AES/CBC/PKCS5Padding");	    
cipher.init(Cipher.ENCRYPT_MODE, key, paramSpec);			    	
byte[] ecrypted = cipher.doFinal(accessKey.getBytes());
accessKey = Base64.encodeToString(ecrypted, Base64.DEFAULT);
\end{lstlisting}

Using that tecnique the \texttt{delegated\_access\_token} is never transmitted over the network. If the delegated phone sends latitude, longitude, timestamp and \texttt{authorization\_key} to the \texttt{REST API [POST] /api/phones/:phoneid/position/delegated} the back-end is able to decrypt \texttt{authorization\_key} using \texttt{delegated\_access\_token} of phone's owner and verify that the owner has authorized the upload of latitude and longitude.

\subsection{\textbf{Communication workflow}}

When on any device running the application an intrusion is detected and no connectivity is available the bluetooth alert workflow starts:\\
\begin{enumerate}
	\item A discovery is started
	\item A listener is registered and each device discovered is stored
	\item At discovery finished for each device the application tries to create a connection, if it fails the device is discarded else a messaging workflow is started:
		\begin{itemize}
			\item An \texttt{HelloMessage} is sent
			\item A \texttt{KeyRequest} is received
			\item The \texttt{access\_key} is build and a \texttt{KeyResponse} is sent
		\end{itemize}
	\item If location is sent correctly 1 hour is waited before next retransmission, else only 1 minute is waited
\end{enumerate}

@@

Images are captured and sent by Android phone in \textit{JPEG} format and are sent and displayed by the web application as they are.\\

@@

>>>>

\title{SecureIt\\
Wireless networks project\\
2012/2013}

\author{
\IEEEauthorblockN{Luca Bonato, Marco Ziccardi}
\IEEEauthorblockA{Corso di studi in Informatica\\
Università degli Studi di Padova\\
Email: \{lohathe,marco.ziccard\}@gmail.com}
}

@@

In order to allow the end user to select the type of monitoring and the type of alerting according to his security needs, CPU and power consumption constraints a configuration panel (shown in figure ref{img:config}) is presented at each start of the application.\\

\begin{figure}[!ht]
\begin{center}
\makebox[\linewidth]{\includegraphics[scale=0.3]{resources/config.png}}
\caption{Configuration view}
\label{img:config}
\end{center}
\end{figure}

\begin{enumerate}
	\item Asks the application to use the accelerometer, shown only if the accelerometer is available on the phone
	\item Asks the application to use the camera, allows to choose wich camera to use and to start the flash
	\item Asks the application to use the microphone
	\item Asks the application to send an SMS to the specified phone number to alert an intrusion
	\item Asks the application to authenticate and send images, audio and location to the back-end (images are sent only if camera has been activated). A username and a password have to be specified
	\item Allows to set the unlock code. Application can be closed only by writing that code
\end{enumerate}

@@

\subsection{Delegated authorization}
In the authentication phase a \texttt{delegated\allowbreak\_access\allowbreak\_token} is retrieved in order to not use the same token for both direct and delegated authentication. However such a token should not be shared with other devices and in order to do so a little protocol has been developed.\\
The protocolo in figure \ref{img:bluetooth} is slightly inspired by Kerberos (\texttt{[1]}) and is based on three messages:\\

@@

When on any device running the application an intrusion is detected and no connectivity is available the bluetooth alert workflow starts:\\
\begin{enumerate}
	\item A bluetooth discovery is started
	\item A listener is registered to the process of discovery and each new device identified is stored
	\item As soon as discovery finishes the application tries to create a connection for each device, if it fails the device is discarded else a messaging workflow is started:
		\begin{enumerate}

			%Hello message
			\item An \texttt{HelloMessage} is sent. It contains a timestamp and the phone's identifier. \texttt{phoneId} is used by the delegated device to know who is requesting delegation, and where to upload location
			%Key request
			\item A \texttt{KeyRequest} is received. It is sent from the delegated device and contains latitude, longitude and a timestamp intended to be sent to the back-end
			%authorization_key creation
			\item An \texttt{authorization\_key} is computed via \texttt{AES} password encryption, using as password the value \texttt{delegated\_access\_token} and encrypting the following \texttt{JSON} string:

			\begin{lstlisting}[language=Java, caption=JSON encrypted with AES]
			{"lat": "latitude",
			 "long": "longitude",
			 "timestamp": "timestamp"}
			\end{lstlisting}

@@

			\begin{lstlisting}[language=Java, caption=AES password encryption]
			SecretKeySpec key = new SecretKeySpec(password.getBytes(), "AES");
			AlgorithmParameterSpec paramSpec = new IvParameterSpec(password.substring(0, 16).getBytes());
			Cipher cipher;
			cipher = Cipher.getInstance("AES/CBC/PKCS5Padding");	    
			cipher.init(Cipher.ENCRYPT_MODE, key, paramSpec);			    	
			byte[] ecrypted = cipher.doFinal(accessKey.getBytes());
			accessKey = Base64.encodeToString(ecrypted, Base64.DEFAULT);
			\end{lstlisting}	
			%Key response
			\item A \texttt{KeyResponse} is sent. It contains the \texttt{authorization\_key} that can be computed only by the requesting client since \texttt{delegated\_access\_token} is never shared
			%Data upload
			\item The delegated phone sends latitude, longitude, timestamp and \texttt{authorization\_key} to the \texttt{REST API [POST] /api\allowbreak/phones\allowbreak/:phoneid\allowbreak/position/delegated}
			%Authorization
			\item The back-end is able to decrypt \texttt{authorization\_key} using \texttt{delegated\_access\_token} of the requesting phone (\texttt{phoneId}) and verify that the owner has authorized the upload of latitude and longitude
		\end{enumerate}
	\item If location is sent correctly 1 hour is waited before next retransmission, else only 1 minute is waited
\end{enumerate}

@@

Images are captured and sent by Android phone in \textit{JPEG} format and are sent and displayed by the web application as they are (as shown in figure \ref{img:slideshow}).\\

\begin{figure}[!ht]
\begin{center}
\makebox[\linewidth]{\includegraphics[scale=0.25]{resources/slideshow.png}}
\caption{Slideshow for captured images}
\label{img:slideshow}
\end{center}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\makebox[\linewidth]{\includegraphics[scale=0.25]{resources/map.png}}
\caption{Map showing last know device position}
\label{img:slideshow}
\end{center}
\end{figure}
